---
title: "Course Project 1"
---

### Introduction

It is now possible to collect a large amount of data about personal movement using activity
 monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices
 are part of the ¡°quantified self¡± movement ¨C a group of enthusiasts who take 
measurements about themselves regularly to improve their health, to find patterns in their
 behavior, or because they are tech geeks. But these data remain under-utilized both
 because the raw data are hard to obtain and there is a lack of statistical methods and 
software for processing and interpreting the data.

This assignment makes use of data from a personal activity monitoring device. This device
 collects data at 5 minute intervals through out the day. The data consists of two months of
 data from an anonymous individual collected during the months of October and November,
 2012 and include the number of steps taken in 5 minute intervals each day.

#### *The variables included in this dataset are:*

* **steps:** Number of steps taking in a 5-minute interval (missing values are NA)

* **date:**  The date on which the measurement was taken in YYYY-MM-DD format

* **interval:** Identifier for the 5-minute interval in which measurement was taken

*The dataset is stored in a comma-separated-value (CSV) file and there are a total of 
17,568 observations in this dataset.*

### **Commit**

##### 1. Code for reading in the dataset 

```{r, echo=TRUE}
df = read.csv('D:\\OneDrive - zju.edu.cn\\Coursera\\R-5\\repdata_data_activity\\activity.csv')
head(df)
```

##### 2. Histogram of the total number of steps taken each day

```{r, echo=TRUE, fig.width=8, fig.height=6}
sum_df = tapply(df[, 'steps'], df[, 'date'], sum)
hist(
     sum_df,
     main = paste("Histogram of ", 'sum step every day'),
     xlab = 'sum step'
     )
```

##### 3. Mean and median number of steps taken each day

* number of steps taken each day

    *beacause of there are too many words to print, so I choose some to print*

```{r, echo=TRUE}
mean_df = tapply(df[, 'steps'], df[, 'date'], mean)
mean_eachday = mean(mean_df)
median_eachday = median(mean_df)
mean_df[1]
mean_df[2]
mean_df[3]
mean_df[4]
mean_df[5]
```

so the mean  of the total number of steps taken per day is `r mean_eachday`, 
the meadian of the total number of steps taken per day is `r median_eachday`.




##### 4. Time series plot of the average number of steps taken

```{r, echo=TRUE}
plot(
     df$interval, df$steps,
     type = 'l'
     )
```

##### 5. The 5-minute interval that, on average, contains the maximum number of steps

```{r, echo=TRUE}
df_s = subset(df, steps == max(df$steps, na.rm = TRUE))
inter = df_s$interval
```

the `r inter` interval that, on average, contains the `r  max(df$steps, na.rm = TRUE)` number of steps

##### 6. Code to describe and show a strategy for imputing missing data
```{r, echo=TRUE}
library(mice)
imp = mice(df)
fit = with(imp, lm(steps ~ date, data = df))
pooled = pool(fit)
result = complete(imp)
df = as.data.frame(result)
head(df)
```
I use the library `mice` to imput the data. I suppose that there is 
a liner relation ship between steps and date

##### 7.Histogram of the total number of steps taken each day after missing values are imputed

```{r, echo=TRUE}
sum_df = tapply(df[, 'steps'], df[, 'date'], sum)
hist(
     sum_df,
     main = paste("Histogram of ", 'sum step every day after imputting'),
     xlab = 'sum step after imputting'
     )
```

##### 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r, echo=TRUE}
library(lubridate)
df_weekend = subset(df, wday(as.Date(df$date, '%Y - %m - %d')) >= 6)
sum_df_weekend = tapply(df_weekend[, 'steps'], df_weekend[, 'date'], sum)
df_weekdays = subset(df, wday(as.Date(df$date, '%Y - %m - %d')) < 6)
sum_df_weekdays = tapply(df_weekdays[, 'steps'], df_weekdays[, 'date'], sum)
```

I sperate the dateset by weekdays

**weekdays**
```{r, echo=TRUE}
head(df_weekdays)
```

**weekends**
```{r, echo=TRUE}
head(df_weekend)
```

The result of the t-test 
```{r, echo=TRUE}
t.test(sum_df_weekend, sum_df_weekdays)
```
we can find that the steps in weekends  *significantly* greater
than steps in weekdays
**weekdays plot**
```{r, echo=TRUE}
plot(
     df_weekdays$date,
     df_weekdays$steps,
     type = 'l'
     )
```

**weekends plot**
```{r, echo=TRUE}
plot(
     df_weekend$date,
     df_weekend$steps,
     type = 'l'
     )
```
